### 2014-07-23 fundamentals/verification.tex
actual ntmanuscript class
more topic sentences

\subsection{Coding Practices}
% What have we done to ensure robustness ?
% Examples from Material class, Transactions, simulation IDs
\subsection{Testing Framework}
% Peer-review system (secretly a note on open source?)
\subsection{Benchmarks}
%Inpro benchmark?
%FCO code-to-code?

>>>>

Unfortunately, we can't wind forward the clock to compare our simulations to 
the futures that we are attempting to model.

However, Cyclus does implement a number of strategies for verification and 
validation of code.

\subsection{Coding Practices}
% What have we done to ensure robustness ?
% Examples from Material class, Transactions, simulation IDs

Some routines are implemented specifically to ensure robustness.

\subsection{Testing Framework}
% Peer-review system (secretly a note on open source?)

We have reasonable test coverage and a code review system.

\subsection{Benchmarks}
%Inpro benchmark?
%FCO code-to-code?

A simple transition scenario recently used for a code-to-code comparison within 
the national laboratories can demonstrate the ability for Cyclus to conform to 
externally defined specifications.
